---
title: "STAT 303 Homework 3"
output: html_document
---

We'll grade your homework by

* opening your "hw3.Rmd" file in RStudio
* clicking "Knit HTML"
* reading the HTML output
* reading your "hw3.Rmd"

You should write R code anywhere you see an empty R code chunk. You
should write English text anywhere you see "..."; please surround it
with doubled asterisks (`**...**`) so that it will show up as boldface
and be easy for us to find.

Include reasonable labels (titles, axis labels, legends, etc.) with
each of your graphs.

Name: Jiapeng Wang

Email: jwang2928@wisc.edu

We'll use data on housing values in suburbs of Boston. They are in an
R package called "MASS." (An R package is a collection of code,
data, and documentation. "MASS" refers to the book "Modern Applied
Statistics with S." R developed from the earlier language, S.) The
MASS package comes with the default R installation, so it's already on
your computer.  However, it's not loaded into your R session by
default. So we'll load it via the `require()` command (there's nothing
for you to do here):

```{r, include=FALSE}
require("MASS")
```

Run `?Boston` (outside this R Markdown document) to read the help page for the `Boston` data frame.

Convert the `chas` variable to a factor with labels "off" and "on" (referring to the Charles river).

```{r}
Boston$chas <- factor(Boston$chas, levels = c(0, 1), labels = c("off", "on"))
```

How many rows are in the Boston data frame? How many columns?

```{r}
cat('The rows in the Boston data frame is', nrow(Boston), '\n')
cat('The columns in the Boston data frame is', length(Boston), '\n')
```

What does a row represent?

**Each row represents an area in the Boston area, and each row contains some information about that area, which can be viewed as a specific sample.**

What does a column represent?

**Each column represents a different variable, and the data in one column shows how different regions differ in one feature dimension.**

Make a density plot (with rug) of tax rates.

```{r}
plot(density(Boston$tax), 
     main = 'density plot of tax rates in Boston',
     xlab = 'tax rates',
     ylab = 'Frequency')
rug(Boston$tax) 
```

Describe the shape of the distribution of tax rates.

**The density map shows two peaks. Around 300 and 700, respectively. And the first peak is bigger.**

Note that the distribution shape doesn't make sense in light of the rug representation of the data. Make a histogram of the tax rates.

```{r}
hist(Boston$tax, breaks="Sturges", freq=NULL,
     main = 'histogram of the tax rates in Boston',
     xlab = 'tax rates',
     ylab = 'Frequency')
```

Why is the second peak of the density plot so large? In what way is the rug representation of the data inadequate? Write a line or two of code to figure it out, and then explain it.

```{r}
hist(Boston$tax,
     breaks = seq(0,900,1),
     main = 'histogram of tax rates in Boston(more precise)',
     xlab = 'tax rates',
     ylab = 'Frequency')
print(Boston$tax[Boston$tax >= 650 & Boston$tax <= 800])
```
**The reason for the large second peak is that the same value 666 occurs many times in the data set.**
**One drawback of rug representation is that the lines will be overlapped when there are many same data, which means you can't get the data distribution from the rug representation.**

Make a barplot of "chas".

```{r}
barplot(table(Boston$chas),
        main = 'Barplot of chas',
        xlab = 'chas',
        ylab = 'Frequency',
        ylim = c(0, 500))
```

How many neighborhoods are on the Charles river?

```{r}
cat('The number of neighborhoods on the Charles River is', sum(Boston$chas == 'on'))
```

Make a single graph consisting of three plots: 

* a scatterplot of "nox" on the y-axis vs. "dis" on the x-axis 
* a (vertical) boxplot of "nox" left of the scatterplot's y-axis
* a (horizontal) boxplot of "dis" below the scatterplot's x-axis

Hint: use `layout()` with a 4x4 matrix, using the top-right 3x3 corner
for the scatterplot, leaving the bottom-left 1x1 corner blank, and
using the other parts for the boxplots.

(An optional challenge, worth 0 extra credit points: remove the axis
and plot border from each boxplot.)

```{r, fig.width=8, fig.height=8}
m = matrix(data=c(2, 1, 1, 1, 2, 1, 1, 1, 2, 1, 1, 1, 4, 3, 3, 3), nrow=4, ncol=4, byrow=TRUE)
layout(m)
plot(Boston$dis, Boston$nox,
     xlab = 'dis',
     ylab = 'nox',
     type = "p") 
boxplot(Boston$nox, axes = FALSE)
boxplot(Boston$dis, horizontal = TRUE, axes = FALSE)
title("scatterplot and boxplot of nox and dis")

```

Look into the highest-crime neighborhood by making a single graph of one column of three rows:

* Find the row number, r, of the neighborhood with the highest "crim".
* Make a density plot of "crim". Include a rug to show the data.
* Add a red circle at (x, y) = (max crime rate, 0) to make this maximum crime rate stand out.
* Make a density plot with rug of "medv", adding a red circle at (x, y) = (medv[r], 0) to see what medv corresponds to the highest crime rate.
* Repeat the last step for "ptratio".

```{r,fig.height=12}
r <- which.max(Boston$crim)
par(mfrow = c(3, 1)) 
plot(density(Boston$crim), 
     main = 'density plot of crim in Boston',
     xlab = 'crim',
     ylab = 'Frequency')
rug(Boston$crim) 
max_crim <- max(Boston$crim)
points(max_crim, 0, col = "red", pch = 20)
legend("top", legend=c("(max crime rate, 0)"), col=c("red"), pch=20)

plot(density(Boston$medv), 
     main = 'density plot of medv in Boston',
     xlab = 'medv',
     ylab = 'Frequency')
rug(Boston$medv) 
points(Boston$medv[r], 0, col = "red", pch = 20)
legend("top", legend=c("(medv[r], 0)"), col=c("red"), pch=20)

plot(density(Boston$ptratio), 
     main = 'density plot of ptratio in Boston',
     xlab = 'ptratio',
     ylab = 'Frequency')
rug(Boston$ptratio) 
points(Boston$ptratio[r], 0, col = "red", pch = 20)
legend("top", legend=c("(ptratio[r], 0)"), col=c("red"), pch=20)
```

What do you notice about the ptratio and medv for the highest-crime neighborhood?

**For medv, Neighborhoods with the highest crime rates had fewer medv values. However, the ptratio of the highest-crime neighborhood is larger. The neighborhoods with the highest crime rates have ptratio values right at the peak of the density plot**
