# STAT 327 Group work on Optimization

Please write the names and email addresses of your group members.
Here's an example:

* Name / email (@wisc.edu only): John Gillett / jgillett@wisc.edu

* Name / email (@wisc.edu only): ...
* Name / email (@wisc.edu only): ...
* Name / email (@wisc.edu only): ...
* Name / email (@wisc.edu only): ...
* Name / email (@wisc.edu only): ...
* Name / email (@wisc.edu only): ...

# Part 1: One-dimensional optimization

Graph the object's altitude vs. time.

```{r}

```

Find the time at which the object strikes the ground.

```{r}

```

Find the object's maximum height.

```{r}

```

Find the time at which the object reaches its maximum height.

```{r}

```

# Part 2: Multi-dimensional optimization

Implement `gradient.descent()`.

```{r}

```

Graph the concentration.

Use `gradient.descent()` to find the peak.

Use `optim()` with `method=Nelder-Mead` to find the peak.

Use `optim()` with `method=BFGS` to find the peak.

How many calls did `optim()` make in each case? Which method would you
expect to be faster?
